---
title: "HW4-tk2886-2021"
author: "Tanvir Khan"
output: pdf_document
---


```{r echo = FALSE, message = FALSE}
library(tidyverse)
```


### Loading the data 
```{r}
crash_df <- 
  read.csv("Crash.csv")
```


### Tidy the data 
```{r warning = FALSE}
crash_dfn <-
  crash_df %>%
  pivot_longer(everything(), 
               names_to = "type_of_accidents",
               values_to = "Values")
```

# Problem 2a
### Generate Descriptive statistics for each group 
```{r warning = FALSE}
#generating descriptive statistics 
crash_df %>% summary()
crash_df %>% summarize_if(is_numeric, sd, na.rm = T)
```

#boxplot
```{r}
#boxplot 
boxplot(Values ~ type_of_accidents, data = crash_dfn,
        main = "Distribution of PTSD score for each type of crash",
        xlab = "Types of Accident",
        ylab = "PTSD Score")
```

### Analysis n Differences Observed:
In the data set that was provided, the mean of the PTSD Score for Pedestrian Incidents is the largest among the three types of accidents. The mean of the PTSD Score of bicycle incidents is the second highest and the mean of the PTSD Scores for car incidents is the lowest. The standard deviation for PTSD score for pedestrian incident is 5.44, the standard deviation for PTSD score in bicycle incident is 4.06, and the standard deviation for the PTSD score for car crash is 3.87. Pedestrian has a larger standard deviation than bicycle and car. This indicates that the PTSD score for this pedestrian incidents is more spread out compared to the other two types if crash. When pedestrians is involved in an incident, their PTSD in generall is more varied compared to the other groups (bicycle and cars). 


# Problem 2b: 
```{r}
res1 = aov(Values ~ factor(type_of_accidents), data = crash_dfn)
summary(res1)
critical_value = qf(0.99, 2, 22)
```
**Interpretation**: 

*Hypothesis:*
Ho: mu1 = mu2 = mu3

Ha: at least two means are not equal 

*Test-Statistics:*
F-Value: 19.53

*Critical Value:*
Critical Value: `r critical_value`

*Decision Intercepted:*
Our F-statistics (19.53) is bigger than our critical value (5.72), we reject the null hypothesis. At 0.01 significance level, we reject the null hypothesis and conclude that at least two true mean PTSD score from the three type of crash groups are different. 


# Problem 2c:
```{r}
# Using Tukey
Tukey_comp = TukeyHSD(res1)
Tukey_comp
plot(Tukey_comp)
```
*Analysis": 



# Problem 2d:







Problem 3b:


```{r}
#test_statistics 
test_statistcs = (15-17.67)^2/17.67 + (18-17.67)^2/17.67 + (20-17.67)^2/17.67 + (18-15.33)^2/15.33 + (15-15.33)^2/15.33 + (13-15.33)^2/15.33
```

```{r}
#critical_value 
critical_value = qchisq(.95, 1)
```


Problem 3c:

Ho: Relapse Status and types of anti-depressant are independent 

Ha: Relase Status and types of anti-depressant are associated/dependent 



