---
title: "HW4-tk2886-2021"
author: "Tanvir Khan"
output: pdf_document
---


```{r echo = FALSE, message = FALSE}
library(tidyverse)
```


### Loading the data 
```{r}
crash_df <- 
  read.csv("Crash.csv")
```


### Tidy the data 
```{r warning = FALSE}
crash_dfn <-
  crash_df %>%
  pivot_longer(everything(), 
               names_to = "type_of_accidents",
               values_to = "Values")
```

# Problem 2a
### Generate Descriptive statistics for each group 
```{r warning = FALSE}
crash_df %>% summary()
crash_df %>% summarize_if(is_numeric, sd, na.rm = T)
```

#boxplot
```{r}
boxplot(Values ~ type_of_accidents, data = crash_dfn,
        main = "Distribution of PTSD score for each type of crash",
        xlab = "Types of Accident",
        ylab = "PTSD Score")
```

### Analysis of Differences Observed:
In the data set that was provided, the mean of the PTSD Score for Pedestrian Incidents is the largest among the three types of accidents. The mean of the PTSD Score of bicycle incidents is the second highest and the mean of the PTSD Scores for car incidents is the lowest. The standard deviation for PTSD score for pedestrian incident is 5.44, the standard deviation for PTSD score in bicycle incident is 4.06, and the standard deviation for the PTSD score for car crash is 3.87. Pedestrian has a larger standard deviation than bicycle and car. This indicates that the PTSD score for this pedestrian incidents is more spread out compared to the other two types if crash. When pedestrians is involved in an incident, their PTSD in general is more varied compared to the other groups (bicycle and cars). 





# Problem 2b: 
```{r}
res1 = aov(Values ~ factor(type_of_accidents), data = crash_dfn)
summary(res1)
critical_value = qf(0.99, 2, 22)
```
**Interpretation**: 

*Hypothesis:*
Ho: mu1 = mu2 = mu3

Ha: at least two means are not equal 

*Test-Statistics:*
F-Value: 19.53

*Critical Value:*
Critical Value: `r critical_value`

*Decision Intercepted:*
Our F-statistics (19.53) is bigger than our critical value (5.72), we reject the null hypothesis. At 0.01 significance level, we reject the null hypothesis and conclude that at least two true mean PTSD score from the three type of crash groups are different. 


# Problem 2c:
```{r}
# Using Tukey's Comparison Adjustment 
Tukey_comp = TukeyHSD(res1)
Tukey_comp
plot(Tukey_comp)
```
*Analysis:* We will be using be Tukey's adjustment since Bonferroni is the most conservative method and gives us less power while Tukey's method controls for all pairwise comparisons and it is less conservative. Based on our Tukey's adjustment method, it is indicated that the the true mean PTSD score for car and bicycle is different since the adjusted p-value for car-bicycle pairwise is 0.00134 which is smaller than our alpha 0.01. Also the the true mean PTSD score for pedestrian and car is different since the adjusted p-value for pedestrian-car pairwise is 0.0000088 which is smaller than our alpha 0.01. Based on the tukey's method, we do not have enough evidence to state that the true mean PTSD score for pedestrian-bicycle pairwise is different. 



# Problem 2d:
Based on the data set provided for each type of crash (bicycle, car, pedestrian), our statistical analysis indicated that the mean PTSD score for pedestrian is 37.88 and the mean PTSD score bicycle crash is 32.5. It has been reported by the National Center for PTSD that a PTSD score of 31-33 or higher suggest the patient may benefit from PTSD treatment. Emergency Department physicians may provide additional resources or a better catered treatment plan to individuals involved in pedestrian and bicycle incidents/crashes for reducing their PTSD symptoms. In our statistical analysis, the mean PTSD score for car is 23.43 and it has been reported by the National Center for PTSD that scores lower than 31-33 may indicate the patient either has sub threshold symptoms of PTSD or does not meet criteria for PTSD, and this information should be incorporated into treatment planning when emergency department professionals are creating a treatment plan that individual's recovery. 






Problem 3b:

```{r}
test_statistcs = (15-17.67)^2/17.67 + (18-17.67)^2/17.67 + (20-17.67)^2/17.67 + (18-15.33)^2/15.33 + (15-15.33)^2/15.33 + (13-15.33)^2/15.33
```

```{r}
critical_value = qchisq(.95, 1)
```


Problem 3c:

Ho: Relapse Status and types of anti-depressant are independent 


Ha: Relase Status and types of anti-depressant are associated/dependent 



